### 2012-05-20 paper/paper.tex
LaTeXed paper

% vim: set tw=79 ft=tex :
\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}

\doublespacing

\title{Backbone-Store: An API for Automating Local Caching of Web Application
Data}
\author{Michael Stunes, Wolfe Styke, Fan (Frances) Zhang}

\begin{document}
\maketitle

\begin{abstract}
Efficiently storing web application data in the client's browser was a
challenging task until the recent HTML5 specification. Web applications that
require fetching the same data that has been previously fetched from a server
can see an improved load time by storing this old data in the client's browser,
requiring only the new data to be retrieved from the server. For our project,
we extended Backbone.js to allow a web developer to easily store and reload a
web application's data using the HTML5 localStorage API. We analyze three
simple applications to study the performance characteristics of loading large
douments, medium-sized emails, and small notes from both the localStorage on
the client's browser and on the server. We find that localStorage performs
faster than loading the same data from th server. This time difference
increases for larger quantities of the same type of item. Since the threshold
for users perceiving lag is about 100 milliseconds, we show that there are
real-world usecases where loading data from a server would cause users to
percieve lag, while loading the same data from localStorage would be percieved
as instantaneous.
\end{abstract}

\section{Introduction}

HTML5 presents new options for storing a web application's data in the client's
browser. The capacity for a web application to efficiently store information
that can be used the next time a user views the website presents two major
benefits. The first benefit is that the web application can store information
that it can use to help speed up the time it takes to present the user
interface for the web application. Users are sensitive to the time it takes a
web application to load, with slower applications causing users to navigate
away or think less of the site. The second benefit is that the web applications
can request less data from a server if it can store information that it
previously would have needed to fetch from the server. This allows a server to
fulfill more requests and thus reduces costs to maintain servers to meet a web
application's requests.

\section{Related Work}

There are several new client-side data storage options for web applications
with HTML5. Web SQL presents a database API similar to SQLite and provides
transactions. However, Web SQL is not supported by all of the major browsers,
with Firefox in particular refusing to ever support Web SQL. There are two
key-value storage options, called sessionStorage and localStorage, that have a
simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
\verb=removeItem(key)=, and \verb=clear()=) for storing key-value pairs.
Session storage stores data only while a user is viewing a website, and
automatically clears the data when a user navigates away from the site. Local
storage persists data until it is deleted by the application or by the user
clearing all of the website's information from the browser. Local storage is
the best solution for cross-browser support and persistent storage.

Backbone-store, the project described in this paper, presents a new way for web
application programmers to easily save their web application's data on the
client to take advantage of the two benefits described above. This project is
an extension of the pure-Javascript Backbone.js library, which is used by many
companies to create web applications for browsers and mobile devices. Data
stored in Backbone.js applications are generally placed in either a Model
object or a Collection object, which is an ordered list of objects of one type
of Model. Backbone.js also provides View objects for managing the UI based on
the state of the Model or Collection objects.

Currently, for a web programmer to store data on the client side while using
Backbone.js, he/she would need to write a custom storage solution to save the
data from each of their models and/or collections to HTML5's localStorage or
another local storage option. Backbone-store simplifies the process of saving
information from a model or collection such that it can be reloaded into the
models and collections the next time the web application starts. With a few new
methods added to the Model and Collection objects, a web developer can choose
when a copy of a model's or collection's data should be stored, and when to
load saved data back into the application's models or collections. There is
also a choice of how the data is stored for collections of models. All models
can be stored as a bundle under one key in the localStorage, or they can be
stored individually, with each model under its own key in the localStorage.
This provides flexibility for different usecases where one option may be
significantly better than the other one depending on the number of items and
the amount of data being stored.

To test our new library to analyze the advantage of using it, we built three
test applications to time how long it takes to load each of three different
size of data items from both the localStorage and the server. We discovered
that the localStorage generally responded faster than a typical server, and
that the difference in response times was more noticeable when larger
quantities of data are being stored.

\section{The Problem Space}

We hypothesize that the browser's HTML5 localStorage persistent data storage
can be used by web applications to increase the speed required to load a web
application's user interface by providing faster access to different types of
items of required information.

Web applications vary in the amount and type of data they must request from a
server before presenting a user interface to a user. Two primary metrics
closely related to our project are the number of individual items requested,
and the size of each of these items. Some applications might require only a few
large items, such as showing a user a menu of large documents they can edit. On
the opposite end of both spectra, a note-taking application might request many
relatively small notes.

HTML5's localStorage presents a key-value storage API for storing a web
application's persistent information, using string keys and string or integer
values. However, Backbone.js collections and models store their data in
Javascript objects. Using the native JSON parse and stringify methods that
convert objects to strings and back again, the library we extend can easily
store the data from the models and collections as strings in localStorage, and
convert the stored strings back to their original object representations.

\section{Solution: Extending Backbone.js}

There are two primary ways to save Backbone.js collections consisting of many
models. One option is to turn the list of models into a JSON string and store
this information under a single key in localStorage. The other option is to
store each model in the collection under its own key. The main tradeoff in
these options is the time it takes to retrieve a single key from localStorage,
and the time it takes to parse a JSON string.

Our library extends Backbone.js by providing these two new persistence storage
options. For a web developer to use these options, the developer chooses a
default persistence strategy for all of their collections of models.
Additionally, the developer can choose a persistence strategy for each
individual collection. This allows the developer to easily specify a single
persistence strategy that will cover the majority of their needs, and only
change the strategy for the minority of collections that will use the
non-default option.

To store a model or a collection's models, a new instance method has been added
to the Backbone.Model and Backbone.Collection options called
``\verb=saveToStore=''. For models, this method simply saves the model's
attributes to the localStorage. For collections, this method uses the
persistence strategy identified by the collection to save the sorted list of
models into the localStorage. To load the data for a model or collection from
localStorage, a new method called ``\verb=loadFromStore='' has been added to
Backbone.Model and Backbone.Collection. For models, this simply loads the data
from localStorage into the model; for collections; this method identifies the
persistence strategy used by the collection and uses the correct retrieval
method to fetch the data from localStorage, parse it back into an array of
models, and add them to the collection.

\section{Contribution}

Our project makes two main contributions. First, we present an API that
automates local caching for web applications. This API will allow developers to
choose from two storage strategies for locally cached data:

\begin{enumerate}
\item Associate one key per collection
\item Associate one key per model in a collection
\end{enumerate}

Second, we conduct a performance evaluation of load and update times for data
stored locally (using the aforementioned two strategies) compared to data
stored remotely for three types of web applications that differ in data size
per item (70 bytes, 900 bytes, 3200 bytes) and data quantity (10, 50, 100, 200,
300 items per collection) and highlight conditions where local storage is most
advantageous.

We find that our API provides superior load and update performance for data
stored locally vs.\ remotely under all data size and quantity conditions except
for the case of loading many small items. Furthermore, we find that our
implementation of local caching exhibits the greatest speedup when data is
stored using the first strategy, with one key-value pair per collection. This
suggests that local caching is most advantageous for applications that load
data of larger size, and moderate to large quantity.

\section{Evaluation}

To evaluate the benefits of Backbone-store, we build three test applications to
understand how our solution handled three different sizes of items requiring
storage. To test large items that might represent a document, we used five
paragraphs of lorem-ipsum, totalling 3265 characters per item. To examine
medium size items such as emails, we used one paragraph of lorem-ipsum,
totallying 905 characters per item. To examine smaller items such as personal
notes, we used a short string of 70 characters. These character lengths are the
length of the JSON string that represents each item. The three applications
performed the same task: load some number of a particular type of item from
localStorage and from the server, separated by a delay so as not to overlap in
execution and skew the load time, and record the load time.

Each of the three web applications records how long it takes the application to
load the data for each of the three test applications. For the time it takes to
load data from the server, the timer is started just before an Ajax request
asks the server for the data. When the data returns from the server, it is
loaded into a Backbone.Collection object, and the timer is stopped after this
is complete. To record the time to load the same data from localStorage, the
timer is started when just before the \verb=loadFromStore= method is called by
a collection. The data is then fetched from localStorage and parsed from a JSON
string into an array of objects, which is then added to the collection before
finally stopping the timer.

We created a simple server using Node.js for our test applications. Our timing
application presented a blank page which loaded a particular number of items
for each of the three types of models into collections from both localStorage
and from server requests. Three request URLs allowed the web application to use
Ajax to query the server for the data needed for each type of model. To easily
collect a large enough sample size of timing data, we had the server record
responses from the web application and print out batches of times for 15
requests to a CSV file. This allowed us to rapidly collect timing data for each
scenario.

\section{Results}

Below we present results that measure the load times of data from both local
storage and the server for three types of applications, listed here, in
decreasing order of data size:

\begin{enumerate}
\item Documents
\item Email
\item Notes
\end{enumerate}

We load the data from each application in varying quantities (10, 50, 100, 200,
300 items per follection) and show that local caching performs faster than data
loaded from the server (except for collections of small items, where the gain
becomes negligible, most likely because of the overhead involved in retrieving
items from the local store).

\begin{figure}[th]
  \centering
  \includegraphics[width=\textwidth]{lines.pdf}
  \caption{Load time as a function of collection size, for each persistence
  method and item size.}
  \label{fig:line}
\end{figure}

Loading large items, such as documents, from the local storage (shown in Figure
\ref{fig:line}A) gives the results that we expect. Load times for both
persistence strategies, and from the server, grow linearly with the number of
items in the collection, and thus with the amount of data retrieved. Both local
persistence methods are faster than retrieving items from the local storage;
the one-key-per-model method is slightly slower than the one-key-per-collection
method due to the additional overhead of retrieving each model from the local
storage separately.

Repeating the same tests with medium-sized items, such as emails (shown in
Figure \ref{fig:line}B), shows similar results; however, the difference in
speed here is less pronounced. This is due to the constant overhead imposed by
accessing the local storage; in the documents example, this overhead is masked
by the linear overhead of retrieving large amounts of data from storage. As in
the previous example, the one-key-per-model method is still slightly slower,
due to additional overhead from retrieving each model from the storage
separately.

Finally, repeating these tests with very small items, such as notes (shown in
Figure \ref{fig:line}C), shows different results: in this case, loading from
local storage is negligibly faster, with the difference becoming smaller for
larger collections. With very small items in the collection, the additional
overhead of the one-key-per-model method becomes large enough to outweigh the
load-time benefits of local storage.

\begin{figure}[th]
  \centering
  \includegraphics[width=\textwidth]{bars.pdf}
  \caption{Load time as a function of item size, for each persistence method
  and two different collection sizes.}
  \label{fig:bar}
\end{figure}

Figure \ref{fig:bar} shows the effect of the size of individual items on the
time to load collections both from storage and from the server. As expected,
load times from the server are generally higher; also, the difference in load
time due to the size of the individual items is much more pronounced when
loading from the server. Differences in load times due to item size for
retrieving collections are much less pronounced when loading from local
storage; again, much of the overhead in loading locally is fixed, and caused
simply by accessing the local store.

\end{document}

### 2012-05-20 paper/paper.tex
Added conclusion to paper

@@
 
+\section{Conclusion}
+
+This report described our extension for the Backbone.js library, which
+simplifies the task of persisting a collection of data models to a web
+browser's local storage, in order to facilitate faster load times and reduced
+server load. This extension provides an API to facilitate saving and loading
+collections on demand, using one of two different persistence strategies. We
+tested our extension using three different demo applications, with different
+characteristics for the data that is being used by the application. Our tests
+varied both the number of data items in a single collection and the size of
+each data itme, to simulate a number of different application scenarios. Our
+tests showed that our extension is effective at reducing the load times in many
+different scenarios, resulting in an improved experience for the application
+user.
+
 \end{document}

### 2012-05-21 paper/paper.tex
Added save-time stuff to paper

@@
 
+Finally, we also tested update times for our two persistence strategies. We did
+this by creating collections with different numbers of items, and measuring the
+time to save each collection to localStorage. Also, to test different save-time
+characteristics of our different persistence strategies, we measured the time
+to resave the collection after adding one model. We predict that the
+one-key-per-model persistence strategy will allow faster updates, by making it
+possible to save only those models that were changed or added since the last
+save.
+
 \section{Results}
@@
 
+\begin{figure}[th]
+    \centering
+    \includegraphics[width=0.7\textwidth]{save.pdf}
+    \caption{Save time as a function of collection size, for each persistence
+    method.}
+    \label{fig:save}
+\end{figure}
+
+Figure \ref{fig:save} shows the elapsed time for saving a collection of
+document-size items into localStorage, while varying the number of items in the
+collection. For both persistence strategies, the time to save the entire
+collection grows linearly with the size of the collection as expected;
+furthermore, the one-key-per-model strategy takes longer to save an entire
+collection, because of the overhead involved in writing many keys to the
+localStorage.
+
+Also, as expected, the time to resave the collection after adding one model is
+much lower (approx. 1 ms in every case) for the one-key-per-model strategy, as
+we are able to save only that model to the localStorage. For the
+one-key-per-collection strategy, the time to save one more model is
+approximately the same as the time to save all of the models, because this
+strategy must write the entire collection to localStorage in either case.
+
 \section{Conclusion}

### 2012-05-21 appserv/server_data/plots.R

@@ -50,3 +50,18 @@ par(mfrow=c(1,2))
 
 barplot(as.matrix(bar.10), names=c('Per-Collection', 'Per-Model', 'Server'), beside=T, legend.text=c('Note', 'Email', 'Document'), ylab='Load time (ms)', main='A. 10-Item Collections', args.legend=list(x='topleft', inset=0.05))
 barplot(as.matrix(bar.300), names=c('Per-Collection', 'Per-Model', 'Server'), beside=T, legend.text=c('Note', 'Email', 'Document'), ylab='Load time (ms)', main='B. 300-Item Collections', args.legend=list(x='topleft', inset=0.05))
+
+
+
+# Save time data
+each.all <- c(4.1, 13.1, 25.033, 48.9, 72.967)
+each.one <- c(0.7, 0.733, 0.933, 1.067, 1.133)
+one.all <- c(2.067, 7.133, 16.5, 32.3, 44.2)
+one.one <- c(1.633, 6.533, 14.9, 30.6, 42.8)
+
+par(mfrow=c(1,1))
+plot(quantities, each.all, type='b', pch=0, xlab='Quantity', ylab='Save Time (ms)', main='Time to Save Collections to Storage')
+lines(quantities, each.one, type='b', pch=1)
+lines(quantities, one.all, type='b', pch=2)
+lines(quantities, one.one, type='b', pch=3)
+legend('topleft', legend=c('Per Model, All', 'Per Model, One', 'Per Coll., All', 'Per Coll., One'), pch=c(0, 1, 2, 3), inset=0.03)

### 2012-05-21 paper/paper.tex
fixed typos

@@
 simple applications to study the performance characteristics of loading large
-douments, medium-sized emails, and small notes from both the localStorage on
-the client's browser and on the server. We find that localStorage performs
-faster than loading the same data from th server. This time difference
+documents, medium-sized emails, and small notes from both the local storage on
+the client's browser and on the server. We find that local storage performs
+faster than loading the same data from the server. This time difference
 increases for larger quantities of the same type of item. Since the threshold
 for users perceiving lag is about 100 milliseconds, we show that there are
-real-world usecases where loading data from a server would cause users to
-percieve lag, while loading the same data from localStorage would be percieved
+real-world use cases where loading data from a server would cause users to
+perceive lag, while loading the same data from localStorage would be perceived
 as instantaneous.
@@
 stored individually, with each model under its own key in the localStorage.
-This provides flexibility for different usecases where one option may be
+This provides flexibility for different use cases where one option may be
 significantly better than the other one depending on the number of items and
@@
 
-Second, we conduct a performance evaluation of load and update times for data
+Second, we conduct a performance evaluation of load times for data
 stored locally (using the aforementioned two strategies) compared to data
@@
 
-We find that our API provides superior load and update performance for data
-stored locally vs.\ remotely under all data size and quantity conditions except
+We find that our API provides superior load performance for data
+stored locally vs.\ remotely under all data sizse and quantity conditions except
 for the case of loading many small items. Furthermore, we find that our
@@
 
-To evaluate the benefits of Backbone-store, we build three test applications to
+To evaluate the benefits of Backbone-store, we built three test applications to
 understand how our solution handled three different sizes of items requiring
 storage. To test large items that might represent a document, we used five
-paragraphs of lorem-ipsum, totalling 3265 characters per item. To examine
-medium size items such as emails, we used one paragraph of lorem-ipsum,
-totallying 905 characters per item. To examine smaller items such as personal
-notes, we used a short string of 70 characters. These character lengths are the
+paragraphs of Lorem ipsum, totaling 3265 characters per item (~3200 bytes). To examine
+medium size items such as emails, we used one paragraph of Lorem ipsum,
+totaling 905 characters per item (~900 bytes) . To examine smaller items such as personal
+notes, we used a short string of 70 characters (~70 bytes). These character lengths are the
 length of the JSON string that represents each item. The three applications
-performed the same task: load some number of a particular type of item from
-localStorage and from the server, separated by a delay so as not to overlap in
-execution and skew the load time, and record the load time.
+performed the same task: 
+\begin{enumerate}
+\item load some number of a particular type of item (e.g., doc, email, note) from
+local storage
+\item load some number of a particular type of item (e.g., doc, email, note) from the server
+\item record the load time.
+\end{enumerate}
+
+Note that 1) and 2) are separated by a delay so as not to overlap in
+execution and skew the load time.
 
@@
 loaded into a Backbone.Collection object, and the timer is stopped after this
-is complete. To record the time to load the same data from localStorage, the
+is complete. To record the time to load the same data from local storage, the
 timer is started when just before the \verb=loadFromStore= method is called by
-a collection. The data is then fetched from localStorage and parsed from a JSON
+a collection. The data is then fetched from local storage and parsed from a JSON
 string into an array of objects, which is then added to the collection before
@@
 
-Finally, we also tested update times for our two persistence strategies. We did
+Finally, we also tested update times for our two local storage strategies. We did
 this by creating collections with different numbers of items, and measuring the
-time to save each collection to localStorage. Also, to test different save-time
+time to save each collection to local storage. Also, to test different save-time
 characteristics of our different persistence strategies, we measured the time
 to resave the collection after adding one model. We predict that the
-one-key-per-model persistence strategy will allow faster updates, by making it
+one-key-per-model local storage strategy will allow faster updates, by making it
 possible to save only those models that were changed or added since the last
@@
 We load the data from each application in varying quantities (10, 50, 100, 200,
-300 items per follection) and show that local caching performs faster than data
+300 items per collection) and show that local caching performs faster than data
 loaded from the server (except for collections of small items, where the gain
@@
 \ref{fig:line}A) gives the results that we expect. Load times for both
-persistence strategies, and from the server, grow linearly with the number of
+local storage strategies, and from the server, grow linearly with the number of
 items in the collection, and thus with the amount of data retrieved. Both local

### 2012-05-21 paper/paper.tex
further changes to abstract

@@
-% vim: set tw=79 ft=tex :
 \documentclass[12pt]{article}
@@
 Efficiently storing web application data in the client's browser was a
-challenging task until the recent HTML5 specification. Web applications that
-require fetching the same data that has been previously fetched from a server
-can see an improved load time by storing this old data in the client's browser,
+challenging task until the recent HTML5 specification. With this new local storage spec, Web applications that require re-fetching the same data from a server
+can see an improved load time by storing old data in the client's browser,
 requiring only the new data to be retrieved from the server. For our project,
-we extended Backbone.js to allow a web developer to easily store and reload a
-web application's data using the HTML5 localStorage API. We analyze three
-simple applications to study the performance characteristics of loading large
+we extended Backbone.js to create our own local caching API to help web developers easily store and reload a web application's data using the HTML5 localStorage API.
+To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading large
 documents, medium-sized emails, and small notes from both the local storage on
-the client's browser and on the server. We find that local storage performs
+the client's browser and from the server. As expected, we find that local storage performs
 faster than loading the same data from the server. This time difference
-increases for larger quantities of the same type of item. Since the threshold
+increases for larger quantities of the same type of item, suggesting that local storage become more advantageous as the amount of loaded data increases. Furthermore, given that the threshold
 for users perceiving lag is about 100 milliseconds, we show that there are
@@
 
-Note that 1) and 2) are separated by a delay so as not to overlap in
+Note that Step 1 and 2 are separated by a delay so as not to overlap in
 execution and skew the load time.

### 2012-05-21 paper/paper.tex
Fixed part about save-time characteristics

@@
 
-Finally, we also tested update times for our two local storage strategies. We did
-this by creating collections with different numbers of items, and measuring the
-time to save each collection to local storage. Also, to test different save-time
-characteristics of our different persistence strategies, we measured the time
-to resave the collection after adding one model. We predict that the
-one-key-per-model local storage strategy will allow faster updates, by making it
-possible to save only those models that were changed or added since the last
+Finally, we also tested update times for our two local storage strategies, by
+creating collections with different numbers of items and measuring the time to
+save each collection to local storage. Also, we believe that our two strategies
+will behave differently in different situations (i.e., saving an entire
+collection for the first time, and saving a collection again after having
+changed or added only a few models); we test this by measuring the time to
+resave the collection after adding one new model. We predict that the
+one-key-per-model local storage strategy will allow faster updates, by making
+it possible to save only those models that were changed or added since the last
 save.

### 2012-05-21 paper/paper.tex
Added bibliography

@@
 \usepackage{graphicx}
+\usepackage{url}
 
@@
 There are several new client-side data storage options for web applications
-with HTML5. Web SQL presents a database API similar to SQLite and provides
+with HTML5. Web SQL \cite{websql} presents a database API similar to SQLite and provides
 transactions. However, Web SQL is not supported by all of the major browsers,
 with Firefox in particular refusing to ever support Web SQL. There are two
-key-value storage options, called sessionStorage and localStorage, that have a
+key-value storage options, called sessionStorage and localStorage \cite{localstorage}, that have a
 simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
@@
 client to take advantage of the two benefits described above. This project is
-an extension of the pure-Javascript Backbone.js library, which is used by many
+an extension of the pure-Javascript Backbone.js \cite{backbone} library, which is used by many
 companies to create web applications for browsers and mobile devices. Data
@@
 
-We created a simple server using Node.js for our test applications. Our timing
+We created a simple server using Node.js \cite{node} for our test applications. Our timing
 application presented a blank page which loaded a particular number of items
@@
 
+\bibliographystyle{plain}
+\bibliography{paper}
+
 \end{document}

### 2012-05-21 paper/paper.tex
changes to related work

--- 2012-05-21 paper/paper.tex
@@
 can see an improved load time by storing old data in the client's browser,
-requiring only the new data to be retrieved from the server. For our project,
-we extended Backbone.js to create our own local caching API to help web developers easily store and reload a web application's data using the HTML5 localStorage API.
+requiring only the new data to be retrieved from the server.
+In this paper, we present Backbone-Store: a local caching API that extends Backbone.js to help web developers easily store and reload a web application's data using the HTML5 localStorage API.
 To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading large
@@
 faster than loading the same data from the server. This time difference
-increases for larger quantities of the same type of item, suggesting that local storage become more advantageous as the amount of loaded data increases. Furthermore, given that the threshold
+increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the amount of data loaded by an application increases.
+Furthermore, given that the threshold
 for users perceiving lag is about 100 milliseconds, we show that there are
@@
 There are several new client-side data storage options for web applications
-with HTML5. Web SQL presents a database API similar to SQLite and provides
+using HTML5. Web SQL presents a database API similar to SQLite and provides
 transactions. However, Web SQL is not supported by all of the major browsers,
-with Firefox in particular refusing to ever support Web SQL. There are two
+with Firefox in particular refusing to ever support Web SQL. [NEED TRANSITION HERE] HTML5 provides two
 key-value storage options, called sessionStorage and localStorage, that have a
@@
 storage persists data until it is deleted by the application or by the user
-clearing all of the website's information from the browser. Local storage is
-the best solution for cross-browser support and persistent storage.
+clearing all of the website's information from the browser.
+In this paper, we use localStorage to implement our local caching strategies because it provides persistent storage (unlike sessionStorage) and is supported by all the major web browsers (unlike Web SQL).
 
@@
 application programmers to easily save their web application's data on the
-client to take advantage of the two benefits described above. This project is
+client side to take advantage of the two benefits described in the Introduction. This project is
 an extension of the pure-Javascript Backbone.js library, which is used by many

### 2012-05-21 paper/paper.tex

@@
 transactions. However, Web SQL is not supported by all of the major browsers,
-with Firefox in particular refusing to ever support Web SQL. [NEED TRANSITION HERE] HTML5 provides two
-key-value storage options, called sessionStorage and localStorage, that have a
-simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
+with Firefox in particular refusing to ever support Web SQL.
+[NEED TRANSITION HERE] HTML5 provides two key-value storage options, called sessionStorage and localStorage, that have a simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
 \verb=removeItem(key)=, and \verb=clear()=) for storing key-value pairs.
@@
 client side to take advantage of the two benefits described in the Introduction. This project is
-an extension of the pure-Javascript Backbone.js library, which is used by many
+an extension of the pure-Javascript Backbone.js \cite{backbone} library, which is used by many
 companies to create web applications for browsers and mobile devices. Data

### 2012-05-21 paper/paper.tex
Tweaked abstract

@@
 requiring only the new data to be retrieved from the server.
-In this paper, we present Backbone-Store: a local caching API that extends Backbone.js to help web developers easily store and reload a web application's data using the HTML5 localStorage API.
+In this paper, we present Backbone-Store: a local caching API that extends Backbone.js to help web developers easily store and reload a web application's data using the HTML5 localStorage API, and two different persistence strategies.
 To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading large
@@
 increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the amount of data loaded by an application increases.
-Furthermore, given that the threshold
-for users perceiving lag is about 100 milliseconds, we show that there are
-real-world use cases where loading data from a server would cause users to
-perceive lag, while loading the same data from localStorage would be perceived
-as instantaneous.
+%Furthermore, given that the threshold
+%for users perceiving lag is about 100 milliseconds, we show that there are
+%real-world use cases where loading data from a server would cause users to
+%perceive lag, while loading the same data from localStorage would be perceived
+%as instantaneous.
+Futhermore, we examined the time required for an application to save data to the local storage, comparing the relative save-time performance of our two persistence strategies, and finding one to be more suitable for small updates to the application's data, and the other to be more suitable for larger updates.
 \end{abstract}

### 2012-05-21 paper/paper.tex
more changes to related work

--- 2012-05-21 paper/paper.tex
@@
 There are several new client-side data storage options for web applications
-using HTML5. Web SQL presents a database API similar to SQLite and provides
+using HTML5. Web SQL provides a database interface similar to SQLite and supports
 transactions. However, Web SQL is not supported by all of the major browsers,
 with Firefox in particular refusing to ever support Web SQL.
-[NEED TRANSITION HERE] HTML5 provides two key-value storage options, called sessionStorage and localStorage, that have a simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
+HTML5 also offers two key-value storage options called sessionStorage and localStorage, that have a simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
 \verb=removeItem(key)=, and \verb=clear()=) for storing key-value pairs. 
@@
 application programmers to easily save their web application's data on the
-client side to take advantage of the two benefits described in the Introduction. This project is
-an extension of the pure-Javascript Backbone.js \cite{backbone} library, which is used by many
-companies to create web applications for browsers and mobile devices. Data
+client side to take advantage of the benefits of local storage (as described in the Introduction).
+This project is an extension of the pure-Javascript Backbone.js \cite{backbone} library, which is used by many companies (e.g., Four Square, Walmart Mobile, Pandora, Trello, etc.) to create web applications for browsers and mobile devices.
+Data
 stored in Backbone.js applications are generally placed in either a Model
@@
 
-Currently, for a web programmer to store data on the client side while using
-Backbone.js, he/she would need to write a custom storage solution to save the
-data from each of their models and/or collections to HTML5's localStorage or
-another local storage option. Backbone-store simplifies the process of saving
-information from a model or collection such that it can be reloaded into the
+Currently, web programmers wishing to employ local caching using Backbone.js would need to write a custom storage solution (including custom libraries and scripts tailored to the particular application) to save the data from each of their models and/or collections to HTML5's localStorage or another local storage option.
+Backbone-store simplifies this process by providing an API that automates the local caching process such that information from a saved model or collection can be reloaded into the
 models and collections the next time the web application starts. With a few new
@@
 also a choice of how the data is stored for collections of models. All models
-can be stored as a bundle under one key in the localStorage, or they can be
-stored individually, with each model under its own key in the localStorage.
-This provides flexibility for different use cases where one option may be
-significantly better than the other one depending on the number of items and
-the amount of data being stored.
-
-To test our new library to analyze the advantage of using it, we built three
-test applications to time how long it takes to load each of three different
-size of data items from both the localStorage and the server. We discovered
-that the localStorage generally responded faster than a typical server, and
-that the difference in response times was more noticeable when larger
-quantities of data are being stored.
+can be stored as a bundle under one key in the localStorage (Strategy 1), or they can be
+stored individually, with each model under its own key in the localStorage (Strategy 2).
+These two local storage options provide flexibility for different use cases where one choice may be
+significantly better than the other, depending on the number of items and
+the amount of data being stored. We evaluate optimal conditions for each strategy in the Results section.
 

### 2012-05-21 paper/paper.tex
Augmented results with 100ms lag

--- 2012-05-21 paper/paper.tex
@@
 
+It is of note that users typically perceive lag in an interface when an
+operation takes more than 100 milliseconds to complete. In all of our tests,
+the key-per-model persistence strategy was able to keep the load time for the
+collection below or very near 100 ms, meaning that users would perceive the
+load time as nearly instantaneous. The load time from the server is much
+higher, so users will perceive noticeable lag while waiting for the application
+to load. This demonstrates that our extension provides application users with
+an improved user experience, due to faster application load times.
+
 \begin{figure}[th]

### 2012-05-21 paper/paper.tex
abstract shortened

--- 2012-05-21 paper/paper.tex
@@
 \begin{abstract}
-Efficiently storing web application data in the client's browser was a
-challenging task until the recent HTML5 specification. With this new local storage spec, Web applications that require re-fetching the same data from a server
+Web applications that require re-fetching the same data from a server
 can see an improved load time by storing old data in the client's browser,
-requiring only the new data to be retrieved from the server.
-In this paper, we present Backbone-Store: a local caching API that extends Backbone.js to help web developers easily store and reload a web application's data using the HTML5 localStorage API, and two different persistence strategies.
-To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading large
-documents, medium-sized emails, and small notes from both the local storage on
-the client's browser and from the server. As expected, we find that local storage performs
+requiring only new data to be retrieved from the server.
+In this paper, we present Backbone-Store: a local caching API that extends Backbone.js and uses the HTML5 localStorage API to offer web developers two different persistent strategies that easily store and reload a web application's data.
+To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading documents, medium-sized emails, and small notes from both the local storage on the client's browser and from the server.
+As expected, we find that local storage performs
 faster than loading the same data from the server. This time difference
 increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the amount of data loaded by an application increases.
-%Furthermore, given that the threshold
-%for users perceiving lag is about 100 milliseconds, we show that there are
-%real-world use cases where loading data from a server would cause users to
-%perceive lag, while loading the same data from localStorage would be perceived
-%as instantaneous.
-Futhermore, we examined the time required for an application to save data to the local storage, comparing the relative save-time performance of our two persistence strategies, and finding one to be more suitable for small updates to the application's data, and the other to be more suitable for larger updates.
+Furthermore, we examine the time required for an application to save data to the local storage, comparing the relative save-time performance of our two persistence strategies, and finding one to be more suitable for small updates to the application's data, and the other to be more suitable for larger updates.
 \end{abstract}
@@
 
-We hypothesize that the browser's HTML5 localStorage persistent data storage
-can be used by web applications to increase the speed required to load a web
-application's user interface by providing faster access to different types of
-items of required information.
+We hypothesize that Backbone-Store can be used by web applications to increase the speed required to load a web application's user interface by providing faster access to items of varying quantity and size.
 
-Web applications vary in the amount and type of data they must request from a
+Web applications vary in both the quantity and type of data they must request from a
 server before presenting a user interface to a user. Two primary metrics

### 2012-05-21 paper/paper.tex
problem space changes

@@
 
-We hypothesize that Backbone-Store can be used by web applications to increase the speed required to load a web application's user interface by providing faster access to items of varying quantity and size.
-
 Web applications vary in both the quantity and type of data they must request from a
@@
 Backbone.Model and Backbone.Collection. For models, this simply loads the data
-from localStorage into the model; for collections; this method identifies the
+from localStorage into the model; for collections, this method identifies the
 persistence strategy used by the collection and uses the correct retrieval
@@
 
-Our project makes two main contributions. First, we present an API that
+Our project makes two main contributions. First, we create an API that
 automates local caching for web applications. This API will allow developers to
-choose from two storage strategies for locally cached data:
+choose from two persistence strategies for locally cached data:
 
@@
 
-We find that our API provides superior load performance for data
-stored locally vs.\ remotely under all data sizse and quantity conditions except
-for the case of loading many small items. Furthermore, we find that our
-implementation of local caching exhibits the greatest speedup when data is
-stored using the first strategy, with one key-value pair per collection. This
-suggests that local caching is most advantageous for applications that load
-data of larger size, and moderate to large quantity.
+We hypothesize that Backbone-Store can be used by web applications to increase the speed required to load a web application's user interface by providing faster access to items of varying quantity and size.
 
@@
 \begin{enumerate}
-\item load some number of a particular type of item (e.g., doc, email, note) from
+\item Load some number of a particular type of item (e.g., doc, email, note) from
 local storage
-\item load some number of a particular type of item (e.g., doc, email, note) from the server
+\item Load some number of a particular type of item (e.g., doc, email, note) from the server
 \item record the load time.
@@
 
-This report described our extension for the Backbone.js library, which
+This report describes our extension for the Backbone.js library, which
 simplifies the task of persisting a collection of data models to a web
-browser's local storage, in order to facilitate faster load times and reduced
+browser's local storage, in order to facilitate faster load times and reduce
 server load. This extension provides an API to facilitate saving and loading
 collections on demand, using one of two different persistence strategies. We
-tested our extension using three different demo applications, with different
-characteristics for the data that is being used by the application. Our tests
-varied both the number of data items in a single collection and the size of
-each data itme, to simulate a number of different application scenarios. Our
-tests showed that our extension is effective at reducing the load times in many
+test our extension using three different demo applications, with different
+characteristics for the data that are being used by the application. Our tests
+vary both the number of data items in a single collection and the size of
+each data item, to simulate a number of different application scenarios. Our
+tests show that our extension is effective at reducing the load times in many
 different scenarios, resulting in an improved experience for the application

### 2012-05-21 paper/paper.tex
Sentence about backbone.js popularity
changes to problem space

@@
 increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the amount of data loaded by an application increases.
-Furthermore, we examine the time required for an application to save data to the local storage, comparing the relative save-time performance of our two persistence strategies, and finding one to be more suitable for small updates to the application's data, and the other to be more suitable for larger updates.
+Furthermore, we examine the time required for an application to save data to the local storage, comparing the relative save-time performance of our two persistence strategies and finding one to be more suitable for small updates to the application's data and the other to be more suitable for larger updates.
 \end{abstract}
@@
 
-Web applications vary in both the quantity and type of data they must request from a
-server before presenting a user interface to a user. Two primary metrics
-closely related to our project are the number of individual items requested,
-and the size of each of these items. Some applications might require only a few
+The first main problem is the diversity of data types stored by web applications. Indeed, Web applications vary in both the quantity (number of items) and size of data they must request from a
+server before loading the user interface, causing possible variance in the load and save times of various persistence strategies.  For example, some applications might require only a few
 large items, such as showing a user a menu of large documents they can edit. On
-the opposite end of both spectra, a note-taking application might request many
+the opposite end of both the quantity and size spectra, a note-taking application might request many
 relatively small notes.
+We address the varying data characteristics by evaluating the load and save times of each persistent strategy for applications using data of varying quantities and sizes and highlight cases where each strategy prevails.
 
-HTML5's localStorage presents a key-value storage API for storing a web
-application's persistent information, using string keys and string or integer
-values. However, Backbone.js collections and models store their data in
-Javascript objects. Using the native JSON parse and stringify methods that
-convert objects to strings and back again, the library we extend can easily
+The second problem is the challenge of transforming application data stored by Backbone.js into a form that readily interfaces with HTML5's localStorage API.
+Whereas Backbone.js stores models and collections as Javascript objects, the HTML5 localStorage requires objects to be represented as string keys and string or integer values.
+We resolve this problem by using the native JSON parse and stringify methods that convert objects to strings and back again, allowing our API to easily
 store the data from the models and collections as strings in localStorage, and

### 2012-05-21 paper/paper.tex
results changes

@@
 \begin{abstract}
-Web applications that require re-fetching the same data from a server
+Web applications that require re-fetching data from a server
 can see an improved load time by storing old data in the client's browser,
@@
 with Firefox in particular refusing to ever support Web SQL.
-HTML5 also offers two key-value storage options called sessionStorage and localStorage, that have a simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
+HTML5 also offers two key-value storage options called sessionStorage and localStorage, which provide a simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
 \verb=removeItem(key)=, and \verb=clear()=) for storing key-value pairs. 
@@
 of Model. Backbone.js also provides View objects for managing the UI based on
-the state of the Model or Collection objects.
+the state of the Model or Collection objects. We used Backbone.js as a base due
+to its aforementioned popularity with many web developers, and because it
+provides a very good model for developers that is easy to modify with our extensions.
 
@@
 models. One option is to turn the list of models into a JSON string and store
-this information under a single key in localStorage. The other option is to
-store each model in the collection under its own key. The main tradeoff in
+this information under a single key in localStorage (Strategy 1). The other option is to
+store each model in the collection under its own key (Strategy 2). The main tradeoff in
 these options is the time it takes to retrieve a single key from localStorage,
@@
 
-Our library extends Backbone.js by providing these two new persistence storage
+Our library extends Backbone.js to provide these two new persistence storage
 options. For a web developer to use these options, the developer chooses a
@@
 To evaluate the benefits of Backbone-store, we built three test applications to
-understand how our solution handled three different sizes of items requiring
+understand how our solution handles three different sizes (70 bytes, 900 bytes, 3200 bytes) of items requiring
 storage. To test large items that might represent a document, we used five
@@
 \item Load some number of a particular type of item (e.g., doc, email, note) from the server
-\item record the load time.
+\item Record the load time.
 \end{enumerate}
@@
 
+We created a simple server using Node.js \cite{node} for our test applications. Our timing
+application presented a blank page which loaded a particular number of items
+for each of the three types of models into collections from both localStorage
+and from server requests. Three request URLs allowed the web application to use
+Ajax to query the server for the data needed for each type of model. To easily
+collect a large enough sample size of timing data, we had the server record
+responses from the web application and print out batches of times for 15
+requests to a CSV file. This allowed us to rapidly collect timing data for each
+scenario.
+
+Measuring Load Time
 Each of the three web applications records how long it takes the application to
@@
 
-We created a simple server using Node.js \cite{node} for our test applications. Our timing
-application presented a blank page which loaded a particular number of items
-for each of the three types of models into collections from both localStorage
-and from server requests. Three request URLs allowed the web application to use
-Ajax to query the server for the data needed for each type of model. To easily
-collect a large enough sample size of timing data, we had the server record
-responses from the web application and print out batches of times for 15
-requests to a CSV file. This allowed us to rapidly collect timing data for each
-scenario.
-
-Finally, we also tested update times for our two local storage strategies, by
+Measuring Save Time
+Finally, we tested save times for our two local storage strategies, by
 creating collections with different numbers of items and measuring the time to
@@
 collection for the first time, and saving a collection again after having
-changed or added only a few models); we test this by measuring the time to
+changed or added only a few models). We test this by measuring the time to
 resave the collection after adding one new model. We predict that the
@@
 \begin{enumerate}
-\item Documents
-\item Email
-\item Notes
+\item Documents (3200 bytes)
+\item Emails (900 bytes)
+\item Notes (70 bytes)
 \end{enumerate}
@@
 items in the collection, and thus with the amount of data retrieved. Both local
-persistence methods are faster than retrieving items from the local storage;
-the one-key-per-model method is slightly slower than the one-key-per-collection
+persistence methods are faster than retrieving items from the local storage.
+The one-key-per-model method is slightly slower than the one-key-per-collection
 method due to the additional overhead of retrieving each model from the local
@@
 speed here is less pronounced. This is due to the constant overhead imposed by
-accessing the local storage; in the documents example, this overhead is masked
+accessing the local storage. In the documents example, this overhead is masked
 by the linear overhead of retrieving large amounts of data from storage. As in
@@
 operation takes more than 100 milliseconds to complete. In all of our tests,
-the key-per-model persistence strategy was able to keep the load time for the
+the key-per-collection persistence strategy was able to keep the load time for the
 collection below or very near 100 ms, meaning that users would perceive the
-load time as nearly instantaneous. The load time from the server is much
-higher, so users will perceive noticeable lag while waiting for the application
+load time as nearly instantaneous. On the other hand, the load time from the server is much
+higher, so users would perceive noticeable lag while waiting for the application
 to load. This demonstrates that our extension provides application users with
@@
 time to load collections both from storage and from the server. As expected,
-load times from the server are generally higher; also, the difference in load
+load times from the server are generally higher. Also, the difference in load
 time due to the size of the individual items is much more pronounced when

### 2012-05-21 paper/paper.tex
Fixed cites, added subheadings

@@
 There are several new client-side data storage options for web applications
-using HTML5. Web SQL provides a database interface similar to SQLite and supports
+using HTML5. Web SQL \cite{websql} provides a database interface similar to SQLite and supports
 transactions. However, Web SQL is not supported by all of the major browsers,
 with Firefox in particular refusing to ever support Web SQL.
-HTML5 also offers two key-value storage options called sessionStorage and localStorage, which provide a simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
+HTML5 also offers two key-value storage options called sessionStorage and localStorage \cite{localstorage}, which provide a simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
 \verb=removeItem(key)=, and \verb=clear()=) for storing key-value pairs. 
@@
 
-Measuring Load Time
+\subsection{Measuring Load Time}
+
 Each of the three web applications records how long it takes the application to
@@
 
-Measuring Save Time
+\subsection{Measuring Save Time}
+
 Finally, we tested save times for our two local storage strategies, by

### 2012-05-21 paper/paper.tex
changes to conclusions

--- 2012-05-21 paper/paper.tex
@@
 requiring only new data to be retrieved from the server.
-In this paper, we present Backbone-Store: a local caching API that extends Backbone.js and uses the HTML5 localStorage API to offer web developers two different persistent strategies that easily store and reload a web application's data.
+In this paper, we present Backbone-Store: a local caching API that extends Backbone.js and uses the HTML5 localStorage API to offer web developers two different persistence strategies that easily store and reload a web application's data.
 To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading documents, medium-sized emails, and small notes from both the local storage on the client's browser and from the server.
-As expected, we find that local storage performs
-faster than loading the same data from the server. This time difference
-increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the amount of data loaded by an application increases.
+As expected, we find that our two implementations of local storage both perform faster than loading the same data from the server, with the one-key-per-collection persistence strategy outperforming the one-key-per-model strategy.
+This time difference increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the amount of data loaded by an application increases.
 Furthermore, we examine the time required for an application to save data to the local storage, comparing the relative save-time performance of our two persistence strategies and finding one to be more suitable for small updates to the application's data and the other to be more suitable for larger updates.
@@
 HTML5 presents new options for storing a web application's data in the client's
-browser. The capacity for a web application to efficiently store information
-that can be used the next time a user views the website presents two major
-benefits. The first benefit is that the web application can store information
-that it can use to help speed up the time it takes to present the user
-interface for the web application. Users are sensitive to the time it takes a
+browser. Efficient local storage presents two major
+benefits. The first benefit is that web applications can store information that is loaded and saved
+frequently to help speed up the time it takes to present the user
+interface. Users are sensitive to the time it takes a
 web application to load, with slower applications causing users to navigate
@@
 stored individually, with each model under its own key in the localStorage (Strategy 2).
-These two local storage options provide flexibility for different use cases where one choice may be
+These two persistence strategies provide flexibility for different use cases where one option may be
 significantly better than the other, depending on the number of items and
-the amount of data being stored. We evaluate optimal conditions for each strategy in the Results section.
+the amount of data being stored. We evaluate the performance of these two strategies in the Results section.
 
@@
 
-The first main problem is the diversity of data types stored by web applications. Indeed, Web applications vary in both the quantity (number of items) and size of data they must request from a
+The first main problem is the diversity of data types stored by web applications. Indeed, Web applications vary in both the quantity and size of data item they must request from a
 server before loading the user interface, causing possible variance in the load and save times of various persistence strategies.  For example, some applications might require only a few
@@
 stored locally (using the aforementioned two strategies) compared to data
-stored remotely for three types of web applications that differ in data size
-per item (70 bytes, 900 bytes, 3200 bytes) and data quantity (10, 50, 100, 200,
+stored remotely for three types of web applications that differ in item size
+per item (70 bytes, 900 bytes, 3200 bytes) and item quantity (10, 50, 100, 200,
 300 items per collection) and highlight conditions where local storage is most
@@
 
-We hypothesize that Backbone-Store can be used by web applications to increase the speed required to load a web application's user interface by providing faster access to items of varying quantity and size.
+We hypothesize that Backbone-Store can be used by web applications to increase the speed required to load a web application's user interface by providing faster access to items of varying quantities and sizes.
 
@@
 application presented a blank page which loaded a particular number of items
-for each of the three types of models into collections from both localStorage
+for each of the three types of models (Documents, Emails, Notes) into collections from both local storage
 and from server requests. Three request URLs allowed the web application to use
@@
 \ref{fig:line}A) gives the results that we expect. Load times for both
-local storage strategies, and from the server, grow linearly with the number of
+local persistence strategies, and from the server, grow linearly with the number of
 items in the collection, and thus with the amount of data retrieved. Both local
@@
 operation takes more than 100 milliseconds to complete. In all of our tests,
-the key-per-collection persistence strategy was able to keep the load time for the
+the one-key-per-collection persistence strategy was able to keep the load time for the
 collection below or very near 100 ms, meaning that users would perceive the
@@
 to load. This demonstrates that our extension provides application users with
-an improved user experience, due to faster application load times.
+an improved user experience, due to noticeably faster application load times.
+Additionally, moving storage from server to client will also reduce the load on the server, allowing it to take more requests from applications, further enhancing its performance and speed.
 
@@
 
-This report describes our extension for the Backbone.js library, which
+This report describes Backbone-Store: our extension for the Backbone.js library, which
 simplifies the task of persisting a collection of data models to a web
 browser's local storage, in order to facilitate faster load times and reduce
-server load. This extension provides an API to facilitate saving and loading
-collections on demand, using one of two different persistence strategies. We
-test our extension using three different demo applications, with different
-characteristics for the data that are being used by the application. Our tests
+server load.
+This extension provides an API that automatically saves and loads collections on demand, using one of two different persistence strategies: one-key-per-model and one-key-per-collection.
+We test our extension using three different demo applications (Documents, Emails, Notes), with different characteristics for the data that are being used by the application.
+Our tests
 vary both the number of data items in a single collection and the size of
-each data item, to simulate a number of different application scenarios. Our
-tests show that our extension is effective at reducing the load times in many
-different scenarios, resulting in an improved experience for the application
-user.
+each data item, to simulate a number of different application scenarios. Finally, our
+test applications show that Backbone-Store is effectively and significantly reduces the load times in many different scenarios, resulting in an improved experience for the application
+user and a more convenient, simpler programming experience for application developers.
 

### 2012-05-21 paper/paper.tex
final

@@
 \begin{abstract}
-Web applications that require re-fetching data from a server
+Web applications that require multiple fetches of the data from the server
 can see an improved load time by storing old data in the client's browser,
 requiring only new data to be retrieved from the server.
-In this paper, we present Backbone-Store: a local caching API that extends Backbone.js and uses the HTML5 localStorage API to offer web developers two different persistence strategies that easily store and reload a web application's data.
-To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading documents, medium-sized emails, and small notes from both the local storage on the client's browser and from the server.
-As expected, we find that our two implementations of local storage both perform faster than loading the same data from the server, with the one-key-per-collection persistence strategy outperforming the one-key-per-model strategy.
-This time difference increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the amount of data loaded by an application increases.
-Furthermore, we examine the time required for an application to save data to the local storage, comparing the relative save-time performance of our two persistence strategies and finding one to be more suitable for small updates to the application's data and the other to be more suitable for larger updates.
+In this paper, we present Backbone-Store: a local caching API that extends Backbone.js and uses the HTML5 localStorage API to provide web developers with two different persistence strategies to easily store and reload an application's data.
+To evaluate the API,  we analyze three simple test applications to measure the performance characteristics of loading documents, medium-sized emails, and small notes from both the local storage on the client's browser and from the server.
+As expected, we find that both persistence strategies perform faster than loading the same data from the server, with the one-key-per-collection strategy outperforming the one-key-per-model strategy.
+This time difference increases for larger quantities of the same type of item, suggesting that local storage becomes more advantageous as the number of items loaded by an application increases.
+Furthermore, we compare the relative saving time performance of our two persistence strategies and find one to be more suitable for small updates to the application's data and the other to be more suitable for larger updates.
 \end{abstract}
@@
 benefits. The first benefit is that web applications can store information that is loaded and saved
-frequently to help speed up the time it takes to present the user
+frequently to help speed up the time it takes to displaythe user
 interface. Users are sensitive to the time it takes a
@@
 of Model. Backbone.js also provides View objects for managing the UI based on
-the state of the Model or Collection objects. We used Backbone.js as a base due
+the state of the Model or Collection objects. We use Backbone.js as a base due
 to its aforementioned popularity with many web developers, and because it
@@
 
-Currently, web programmers wishing to employ local caching using Backbone.js would need to write a custom storage solution (including custom libraries and scripts tailored to the particular application) to save the data from each of their models and/or collections to HTML5's localStorage or another local storage option.
+Currently, web programmers wishing to employ local caching using Backbone.js need to write a custom storage solution (including custom libraries and scripts tailored to the particular application) to save the data from each of their models and/or collections to HTML5's localStorage or another local storage option.
 Backbone-store simplifies this process by providing an API that automates the local caching process such that information from a saved model or collection can be reloaded into the
@@
 
-The first main problem is the diversity of data types stored by web applications. Indeed, Web applications vary in both the quantity and size of data item they must request from a
+The first main problem is the diversity of data stored by web applications. Indeed, Web applications vary in both the quantity and size of data item they must request from a
 server before loading the user interface, causing possible variance in the load and save times of various persistence strategies.  For example, some applications might require only a few
 large items, such as showing a user a menu of large documents they can edit. On
-the opposite end of both the quantity and size spectra, a note-taking application might request many
+opposite ends of the quantity and size spectra, a note-taking application might request many
 relatively small notes.
@@
 
-Our project makes two main contributions. First, we create an API that
+We hypothesize that Backbone-Store can be used by web applications to increase the speed required to load a web application's user interface by providing faster access to items of varying quantities and sizes.
+
+To prove our hypothesis, this project makes two main contributions. First, we create an API that
 automates local caching for web applications. This API will allow developers to
@@
 300 items per collection) and highlight conditions where local storage is most
-advantageous.
-
-We hypothesize that Backbone-Store can be used by web applications to increase the speed required to load a web application's user interface by providing faster access to items of varying quantities and sizes.
+advantageous. We also evaluate how long it takes for a collection of varying numbers of items to be saved to local storage, noting which persistence strategy performs better.
 
@@
 
-Note that Step 1 and 2 are separated by a delay so as not to overlap in
-execution and skew the load time.
+(Note that Step 1 and 2 are separated by a delay so as not to overlap in
+execution and skew the load time.)
 
@@
 an improved user experience, due to noticeably faster application load times.
-Additionally, moving storage from server to client will also reduce the load on the server, allowing it to take more requests from applications, further enhancing its performance and speed.
+Additionally, moving storage from server to client will reduce the load on the server, allowing it to take more requests from applications, further enhancing its performance and speed.
 
@@
 each data item, to simulate a number of different application scenarios. Finally, our
-test applications show that Backbone-Store is effectively and significantly reduces the load times in many different scenarios, resulting in an improved experience for the application
-user and a more convenient, simpler programming experience for application developers.
+test applications show that Backbone-Store effectively and significantly reduces the load times in many different scenarios, resulting in an improved experience for the application
+user while simplifying the local caching programming process for application developers.
 
